Spatial Reasoning and Statistical Graphics

### 2014-10-30 Paper/Draft1/TestingVisualAptitude.Rnw
Move figure around
Transition paragraph

>>>>

\newtext{Next, we examine the effect of demographic factors on lineup performance. Previous work found a relationship between lineup performance and factors such as education level, country of origin, and age\cite{humanfactorslineups}; our participant population is more homogeneous, which allows us to explore factors such as educational background and skills on performance in lineup tests. }
